### 2017-06-16 Manuscripts/cog-psych/cogpsych.tex
added kjk passages, ready for joe's lookover

\subsection{Similarity and Contrast in Cognition}
The proposal that category contrast is a primary constraint in creative generation is, in some ways, entirely commonsense. To successful create something \textit{new}, it must be different from what is known. Beyond its role in creative generation, category contrast is also of fundamental importance in categorization more broadly. All other factors held constant, new categories are easier to learn if they are dissimilar to members of other categories, and knowledge of highly distinct categories is applied more accurately than that of ill-defined categories \citep{ashby1994categorization,imai1965discriminability}. Likewise, basic-level categories \citep{rosch1976basic} are thought to be abstracted in order to maximize within-category similarity while minimizing between-category similarity. Finally, the act of forming category representations affects similarity judgments about category members and nonmembers, with category members being viewed as more similar to one another than members of other categories \citep{goldstone1994influences,goldstone2001altering}.

@@

>>>>

\subsection{Similarity and Contrast in Cognition}

The proposal that category contrast is a primary constraint in creative generation is, in some ways, entirely commonsense. To successful create something \textit{new}, it must be different from what is known. Beyond its role in creative generation, category contrast is also of fundamental importance in categorization more broadly. All other factors held constant, new categories are easier to learn if they are dissimilar to members of other categories, and knowledge of highly distinct categories is applied more accurately than that of ill-defined categories \citep{ashby1994categorization,imai1965discriminability}. Likewise, basic-level categories \citep{rosch1976basic} are thought to be abstracted in order to maximize within-category similarity while minimizing between-category similarity. Finally, the act of forming category representations affects similarity judgments about category members and nonmembers, with category members being viewed as more similar to one another than members of other categories \citep{goldstone1994influences,goldstone2001altering}.

@@

\subsection{Implications For Categorization}

Although our work has mainly addressed the processes involved in the creative generation of  concepts, in this paper we have studied these processes as they apply within an artificial categorization domain. By consequence, our findings also provide an advance in our understanding categorization more broadly.

Categorization research addresses the representations and processes that underlie the learning and use of categories. Category learning tasks are generally about figuring out which items belong to which category. Once learned, categories are generally used to classify new stimuli and to make inferences beyond the available information. Our work is fairly unique in that people learn a single category through positive examples and then figure out another category that would make sense in the domain. In other words, only one category is provided to be learned and the use that is required of that category is to generate a contrast category. Such propagating of categories (producing one from another) may not seem like a fundamental or ubiquitous cognitive activity, but consider navigating a highly unfamiliar environment —  it would be practical, perhaps even critical, to generate expectations about what other kinds of things you are likely to encounter based on those that you already have. In the present studies, we have learned something about the form that such expectations are likely to take.

We can think of the category generation task in our studies as asking a person to formulate an idea about what set of items in the domain are most interestingly not members of the original category. To meet this condition, the items must take some form of coherence that aligns with that of the original category and some form of distinctiveness relative to the original category. Reflecting the basic level of organization in natural categories, it makes sense to generate a set of items that possess strong within-category coherence (by importing or systematically transforming the internal structure of the original category) as well as strong between-category differentiation (by creating maximum contrast with the original category). In this sense one can see the patterns of performance in the category generation task as recapitulating the order of semantic organization.
